Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-14 ICML-submission/related-work.tex
initial related work

The problem of bandit multiclass linear classification was initially formulated
in the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
two computationally inefficient algorithms that work in the standard
linearly separable setting, one with a mistake bound of $O(K^2 d
\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in the margin parameter can be obtained.

>>>>

The problem of online bandit multiclass learning was initially formulated
in the pioneering work of~\cite{Auer-Long-1999}, under the name of
``weak reinforcement model''. They show that if the set of examples shown is
separable by a classifier in a prespecified hypothesis class $\calH$, then the optimal
 mistake bound in the bandit setting can be upper bounded by the optimal mistake
 bound in the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
 (See~\cite{Long-2017} for improvements of the factor to $(1 + o(1)) K \ln K$.)
 ~\cite{Daniely-Helbertal-2013} extend the results to the setting where the
 performance of the algorithm is measured by its regret, i.e. the difference
 between the number of mistake made by the algorithm and the number of mistake
 made by the best classifier in $\calH$ in hindsight. However, all algorithms developed in
 this context are computationally inefficient.

The linear classification version of this problem
is initially studied by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
two computationally inefficient algorithms that work in the standard
linearly separable setting, one with a mistake bound of $O(K^2 d
\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in the margin parameter can be obtained.
